Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
Wording
Minor wording (if -> whether)
Resolve a TBD

We propose to use Doctest and Haddock for evidence that is useful as
user documentation, and Hspec for evidence that is not useful as user
documentation.

\begin{quote}
    TBD: Not correct English, so we have to find an other way to say
    this.

    The following subsections disccuss problems when we try to carry
    out our proposal of BDD.
\end{quote}

@@

\noindent Though code blocks in Haddock comments are a useful feature,
we still think that this particular usage has problems.  The code
block contains a property.  And it would be useful to have a tool that
automatically extracts and tests the property.
But writing such a tool is hard, because it is not easy to decide if
the code block is a property, an example, or some random code snippet.

>>>>

We propose to use Doctest and Haddock for evidence that is useful as
user documentation, and Hspec for evidence that is not useful as user
documentation.  The following subsections discuss problems that we
have to solve before we can do this.

@@

\noindent Though code blocks in Haddock comments are a useful feature,
we still think that this particular usage has problems.  The code
block contains a property.  And it would be useful to have a tool that
automatically extracts and tests the property.
But writing such a tool is hard, because it is not easy to decide
whether the code block is a property, an example, or something else.
